Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-04 cordillera-cycle.tex
Enhance ice cover duration plot.

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           Aside the location of present-day ice caps, note the persistence of
           a central ice dome over the Skeena mountains during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           corresponds to short durations of ice cover along most of the
           margin.
           \note{I am trying to improve the readability of low ice cover
           duration values on this figure.}}
  \label{fig:duration}
\end{figure}

>>>>

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           A contiguous ice cover spanning from the Alaska Range (AR) to the
           southern Coast Mountians (CM) and Rocky Mountains (RM) exists for
           about 28\,\unit{kyr} in the GRIP simulation and about 29\,\unit{kyr}
           in the EPICA simulation. Note the irregular colour scale. A central
           ice cover persists over the Skeena Mountains (SM) during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           generally corresponds to relatively short durations of ice cover.
  \label{fig:duration}
\end{figure}
